Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-12-22 hscc2017/paper.tex
prep for final version
line breaks

\documentclass{sig-alternate-05-2015}

@@

\renewcommand{\baselinestretch}{0.975}
\include{macros}

@@

 \end{tikzpicture}
}
\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
\label{fig:CEGIS}}
\end{figure*}
%
%
In more detail, in the first stage, denoted by {\sc Uncertainty} in
Figure~\ref{fig:CEGIS}, assuming a precision \param{I_p}{F_p} we check
whether the system is unstable for the current candidate solution, i.e., if
$\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.  If this is the
case, then we obtain a counterexample $\tilde G(z)$,
%
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
%
which makes the closed-loop system unstable.  This uncertainty is added to
the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, we
obtain a candidate solution consisting of a controller $C(z)$, which makes
the closed-loop system stable for all the uncertainties accumulated in {\sc
inputs}.

>>>>

\documentclass[final]{sig-alternate-05-2015}

@@

%\renewcommand{\baselinestretch}{0.975}
\allowdisplaybreaks
\include{macros}

@@

 \end{tikzpicture}
}
\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
\label{fig:CEGIS}}
\end{figure*}
%
%
In more detail, in the first stage, denoted by {\sc Uncertainty} in
Figure~\ref{fig:CEGIS}, assuming a precision \param{I_p}{F_p} we check
whether the system is unstable for the current candidate solution, i.e., if
$\neg \phi_\mathit{stability}$ is satisfiable for~$S(z)$.  If this is the
case, then we obtain a counterexample~$\tilde G(z)$,
%
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
%
which makes the closed-loop system unstable.  This uncertainty is added to
the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, we
obtain a candidate solution consisting of a controller $C(z)$, which makes
the closed-loop system stable for all the uncertainties accumulated in {\sc
inputs}.
